pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-06 manuscript/greenwell.tex
minor tweaks

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Constructing PDPs in R
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Constructing PDPs in R}

@@

For illustration, we return to the Boston housing data. The example below, fits an \pkg{xgboost} model; the tuning parameters were predetermined using 5-fold cross-validation. (Make sure you are using the latest version of \pkg{xgboost}: \url{https://github.com/dmlc/xgboost/tree/master/R-package}.)
\begin{example}
set.seed(102)
boston.xgb <- xgboost(data = data.matrix(subset(boston, select = -cmedv)),
                      label = boston$cmedv, objective = "reg:linear",
                      nrounds = 2000, max_depth = 3, eta = 0.01)
\end{example}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Constructing PDPs in R
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Constructing PDPs in R}
\label{sec:boston}

@@

For illustration, we return to the Boston housing data. The code chunk below fits an \pkg{xgboost} model to the \code{boston} data frame from Section~\ref{sec:boston}; the tuning parameters were predetermined using 5-fold cross-validation. (Make sure you are using the latest version of \pkg{xgboost}: \url{https://github.com/dmlc/xgboost/tree/master/R-package}.)
\begin{example}
set.seed(102)
boston.xgb <- xgboost(data = data.matrix(subset(boston, select = -cmedv)),
                      label = boston$cmedv, objective = "reg:linear",
                      nrounds = 2000, max_depth = 3, eta = 0.01)
\end{example}
